\documentclass[12,twoside]{mammeTFM}
%\usepackage[active]{srcltx}
\usepackage{amsthm,amsmath,amssymb,amsfonts,amscd}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage[all]{xy}
\usepackage{booktabs}
\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{float}

\usetikzlibrary{shapes}
\usetikzlibrary{positioning}
%\usepackage[usenames]{xcolor}
%\usepackage{fancyhdr}

%%%%%Author packages if necessary


% Theorem Environments: add extra ones at the end if you need it.

\newtheorem*{theoremA}{Theorem A}
\newtheorem{theorem}{Theorem}[section]

\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem*{remarknonumber}{Remark}
\newtheorem{observation}[theorem]{Observation}




%%%%%%%%%%%%%%%%%%
% macros/abbreviations: Include here your own.
%%%%%%%%%%%%%%%%%%

\newcommand{\N}{\ensuremath{\mathbb{N}}}


% Body of document

\titol{A Remotely-driven Hoverboard \\[3mm] With Platform Leaning Control}
\titolcurt{Leaning Control}
\authorStudent{Esteve Tarrag\'o}
\supervisors{Advisor: Enric Celaya, Tutor: Merc\`e Oll\`e}
\monthYear{September, 2019}

%\msc[2010]{Primary  	55M25, 57P10, Secondary 55P15, 57R19, 57N15.}

\paraulesclau{Dynamic, System, Control, Design}
\agraiments{
I would first like to thank my thesis advisor Prof. Enric Celaya. Enric was always 
open whenever I ran into a trouble spot or had a question about my research or 
writing. He consistently allowed this thesis to be my own work, but steered me in 
the right the direction whenever he thought I needed it.

I would also like to thank  Prof. Llu\'is Ros who was also advising me through
the first steps of the design and always gave constructive feedback.

Also this project wouldn't have been possible without my lab co-workers. I would
like to highlight three of them: I\~nigo Moreno, Sergi Hernandez and Patrick Grosch.
They teached my all kind of stuff and I am very grateful for their time.

This research opportunity was possible thanks to IRI (Institut de Robòtica i Informàtica
Industrial). They facilited my a workstation, material and a fantastic
workshop where to build my robot.
}


\abstracteng{
    This thesis is centered arround the design, construction and control of a 
    remote hoverboard. The main challenge of this project is the study of the 
    leaning control of the hoverboard platform and the restrictions it induce.

    Nowadays segways are a popular way of human transportation and there also exist segway robots. 
    Both, human-driven and autonomus segway robots have their speed determined by their inclination.
    (e.i. If you wish to go forward in a segway you should put your weight in the same direction).
    So in this systems the inclination is not a degree of freedom but a compulsary consequence from moving.
    Unblocking this degree of freedom may help two-wheel robots perform new task as mesurments, taking images 
    or samples from other inclinations, avoiding obstacles, etc.

    We have studied diferrent mechanisms to control the leaning while allowing the movement of the robot.
    Then we studied the dynamics of our system to deterimine it's dimensions and create an optimal design
    accordingly. We have also run simulations with different policies to see how our system would evolve.
    
    Finally we builded and programmed our robot so it can be remotely controlled from anywhere.
}

%%%%%%%%%
\begin{document}
\maketitle
\newpage
\tableofcontents

\include{purpose}
\include{design}
\include{mechanical_study}
\include{optimization}
\include{flywheel_study}
\include{dynamic_study}
\include{components}
\include{control}
\include{software}
\include{conclusion}

\end{document}